\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
fixed figure ref
Bug fixes

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{6point.pdf}
\caption{Graph of zones, populations, and travel times}
\end{center}
\label{fig:fullgraph}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{greedy6point.pdf}
\caption{Graph as in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
\end{center}
\end{figure}

@@

\subsubsection{$n=2$}
We ran the greedy algorithm for $n=2$ and we got that ambulances should be placed in zones
2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
zone 1, and none of zone 3.

\subsubsection{$n=1$}
We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 5. This arrangement allows the single ambulance to cover all of zone 4-6.

>>>>

\begin{figure}[htbp]
\label{fig:fullgraph}
\begin{center}
\includegraphics[width=3in]{6point.pdf}
\caption{Graph of zones, populations, and travel times}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{greedy6point.pdf}
\caption{Graph in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
\end{center}
\end{figure}

@@

\subsubsection{$n=2$}
We ran the greedy algorithm for $n=2$ and we got that ambulances should be placed in zones
2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
zone 1, and half (28333/55000) of zone 3.

\subsubsection{$n=1$}
We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 2.
This arrangement allows the single ambulance to cover all of zone 2, half (25000/5000) of zone 1,
and half (28333/55000) of zone 3.

For all of these scenarios, our greedy heuristic got the exact same answer as the
brute-force algorithm, guaranteeing an optimal answer, which indicates that our greedy heuristic
is good. %TODO make sound good
